### 2013-07-15 tests_Housing.Rmd
more results into latex
scaling all datasets, using 25 runs, lambda 0.8

library(ggplot2)

@@

size <- length(report$ga.error)
list.data <- list(error=c(report$ga.error, 
                          report$lm.error,
                          report$svm.error,
                          report$rpart.error,
                          report$rf.error,
                          report$citree.error), 
                  method=c(rep("GA.Poly",size),
                           rep("Lin.Reg.",size),
                           rep("SVM",size), 
                           rep("RPART",size),
                           rep("Rnd.For.",size),
                           rep("CI.Tree",size)))

@@

qplot(method,error,data=df,geom=c("jitter","boxplot")) + 
  ylab("root-mean-square error") + 
  xlab("regression method") +
  ggtitle("Housing dataset")

>>>>

@@

library(ggplot2)
size <- length(report$ga.error)
list.data <- list(error=c(report$ga.error, 
                          report$lm.error,
                          report$svm.error,
                          report$rpart.error,
                          report$rf.error,
                          report$citree.error), 
                  method=c(rep("GA.Poly",size),
                           rep("Lin.Reg.",size),
                           rep("SVM",size), 
                           rep("RPART",size),
                           rep("Rnd.For.",size),
                           rep("CI.Tree",size)))

@@

qplot(method,error,data=df,geom=c("jitter","boxplot")) + 
  ylab("root-mean-square error") + 
  xlab("regression method") +
  coord_cartesian(ylim = c(0.2, 0.75))  +
  ggtitle("Housing dataset")

### 2013-07-15 tests_Kinematics.Rmd
made some graphics
more results into latex
scaling all datasets, using 25 runs, lambda 0.8

sapply(my.data, class)
# my.data$x1 <- as.numeric(my.data$x1) # x1 was a factor, make it a numeric value
head(my.data,8)

@@

source("gapolyfuncs.R")
report <- make.report(my.data, population=200, iterations=100)

@@

save(report, file="Kinematics200.Rda") # recover with load("Kinematics.Rda")

@@

write.table(df, "Kinematics300.txt")

>>>>

sapply(my.data, class)
# my.data$x1 <- as.numeric(my.data$x1) # x1 was a factor, make it a numeric value
my.data <- as.data.frame(scale(my.data))
head(my.data,8)

@@

source("gapolyfuncs.R")
report <- make.report(my.data, population=300, iterations=100, runs=25, lambda=0.8)

@@

save(report, file="Kinematics300_lambda0.8_25runs.Rda") # recover with load("Kinematics.Rda")

@@

write.table(df, "Kinematics200.txt")

### 2013-07-15 texts/experiments.tex
more results into latex
scaling all datasets, using 25 runs, lambda 0.8

In order to train and test the performance of GApoly it was used several datasets (see below). For each dataset, we selected 70\% for training purposes and the remaining observations to make the test set in order to compute the estimated rmse. To achieve more robust results, for each dataset there were ten runs, each one with different samples for the train and test sets. The results below are boxplots for the test set error predictions over these different runs.

@@

\begin{figure}[htb]
	\begin{center}
		\includegraphics[height=6cm,width=10cm,angle=0]
			{figures/Housing_dataset_lambda0.975.eps}
		\caption{results for Boston Housing dataset}
	\end{center}
\end{figure}

@@

\begin{figure}[htb]
	\begin{center}
		\includegraphics[height=6cm,width=10cm,angle=0]
			{figures/Abalone_dataset_lambda1.0.eps}
		\caption{results for Abalone dataset}
	\end{center}
\end{figure}

@@

\begin{center}
\begin{tabular}{cccccccc}
x1 & x2 & x3 & x4 & x5 & x6 & x7 & y \\
8 & 307 & 17 & 3504 & 12.0 & 70 & 1 & 18 \\
8 & 350 & 35 & 3693 & 11.5 & 70 & 1 & 15 \\
8 & 318 & 29 & 3436 & 11.0 & 70 & 1 & 18 \\
8 & 304 & 29 & 3433 & 12.0 & 70 & 1 & 16 \\
8 & 302 & 24 & 3449 & 10.5 & 70 & 1 & 17 
\end{tabular}
\end{center}

\begin{figure}[htb]
	\begin{center}
		\includegraphics[height=6cm,width=10cm,angle=0]
			{figures/Auto-Mpg_dataset_lambda0.8.eps}
		\caption{results for Auto-MPG dataset}
	\end{center}
\end{figure}

% The best polynomial, with a rmse of 2.15 for the test set, was

% $$y = -3.4 10^{-6} x_4 x_6^2 + 1.05 10^{-8} x_6^5 + 33.7$$

>>>>

In order to train and test the performance of GApoly it was used several datasets (see below). For each dataset, we selected 70\% for training purposes and the remaining observations to make the test set in order to compute the estimated rmse. To achieve more robust results, for most datasets there were 25 runs, each one with different samples for the train and test sets. For the datasets with attribute values of different magnitudes, a preliminary scaling was executed. The results below are boxplots for the test set error predictions over these different runs.

@@

\begin{figure}[htb]
	\begin{center}
		\includegraphics[height=6cm,width=10cm,angle=0]
			{figures/Housing_dataset_lambda0.8_25runs.eps}
		\caption{results for Boston Housing dataset}
	\end{center}
\end{figure}

Just as an example of the model the GApoly algorithm outputs: in this dataset the best polynomial, with a rmse of 0.38 for the test set, was the following:

$$y = -0.12 x_6 x_9^4 + 0.78 x_6 - 0.4 x_9^2 x_{13} + 0.17 x_{13}^2 - 0.044$$

where the attributes mean:
$x_6$, RM average number of rooms per dwelling;
$x_9$, RAD index of accessibility to radial highways;
$x_{13}$, Lower status of the population.

@@

\begin{figure}[htb]
	\begin{center}
		\includegraphics[height=6cm,width=10cm,angle=0]
			{figures/Abalone_dataset_lambda0.8_25runs.eps}
		\caption{results for Abalone dataset}
	\end{center}
\end{figure}

% best polynomial, rsme 0.65
% $$y = 0.52 s_1^2 x_5 - 0.13 x_2 x_8 -0.75 x_1^2 x_6 + 0.78 x_8 + 0.18 $$

@@

\begin{figure}[htb]
	\begin{center}
		\includegraphics[height=6cm,width=10cm,angle=0]
			{figures/Auto-Mpg_dataset_lambda0.8_25runs.eps}
		\caption{results for Auto-MPG dataset}
	\end{center}
\end{figure}

% best polynomial, rmse 0.32
%$$ y = 0.4 x_6 + 0.02 x_5^3 x_6 - 0.85 x_4 + 0.23 x_4^2 - 0.26 $$
